---
title: "data_analysis"
author: "Shari Tian"
date: "2/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages

```{r}
library(tidyverse)
library(broom)
library(sf)
library(lme4)

exponentiate <- function(x) exp(x) 

```

# Model for Zimbabwe

## Loading data

```{r}
zimbabwe <- readRDS("DHS_data/Zimbabwe/Zimbabwe_final.RDS")
zimbabwe <- zimbabwe %>%
  select(c(abortion, conception, start, start_modern, start_trad, 
           start_short, start_long, shortLong_switch, longShort_switch, 
           modTrad_switch, tradMod_switch, discontinuation, time, Year, 
           exposed_15, v001, deaths, foreign_aid, v501, v013, v025, v149, 
           v190, cluster_unique)) %>%
  mutate(v501=as.character(v501),
         v013=as.character(v013),
         v025=as.character(v025),
         v149=as.character(v149),
         v190=as.character(v190)) %>%
  mutate(time = fct_relevel(time, ref = "During"),
         deaths = ifelse(is.na(deaths) == TRUE, 0, deaths))
```

## Running models

```{r}
outcomes <- c("abortion", "conception", "start", "start_modern", 
              "start_trad", "start_short", "start_long", 
              "shortLong_switch", "longShort_switch", "modTrad_switch",
              "tradMod_switch", "discontinuation")

for (i in 1:length(outcomes)) {
  country <- "zimbabwe"
  zimbabwe$outcome <- zimbabwe[[outcomes[i]]]
  print(paste0("Running...", outcomes[i]))
  model <- tidy(lm(outcome ~ 
            time*exposed_15 + 
            #cluster_unique +
            foreign_aid + 
            v501 + 
            v013 + 
            v025 + 
            v149 + 
            deaths + 
            v190, 
            data = zimbabwe))
    # model_glm <- lmer(outcome ~ 
    #         time*exposed_15 + 
    #         foreign_aid + 
    #         v501 + 
    #         v013 + 
    #         v025 + 
    #         v149 + 
    #         deaths + 
    #         v190 +
    #         (1|cluster_unique), 
    #         data = zimbabwe)
  model <- model %>%
  filter(str_detect(term, "time") == TRUE)
  write.csv(model, file = paste0("Results/", country, "_", outcomes[i], ".csv"))
}

# stargazer(model_glm,
#           type="text",
#           ci=T,
#           apply.coef = exponentiate,
#           apply.ci = exponentiate)


```


# Model for Mali

## Loading data

```{r}
mali <- readRDS("DHS_data/Mali/Mali_final.RDS")
mali <- mali %>%
  select(c(abortion, conception, start, start_modern, start_trad, 
           start_short, start_long, shortLong_switch, longShort_switch, 
           modTrad_switch, tradMod_switch, discontinuation, time, Year, 
           exposed_15, v001, deaths, foreign_aid, v501, v013, v025, v149, 
           v190, cluster_unique)) %>%
    mutate(v501=as.character(v501),
         v013=as.character(v013),
         v025=as.character(v025),
         v149=as.character(v149),
         v190=as.character(v190)) %>%
  mutate(time = fct_relevel(time, ref = "During"),
         deaths = ifelse(is.na(deaths) == TRUE, 0, deaths))
```

## Running models

```{r}
outcomes <- c("abortion", "conception", "start", "start_modern", 
              "start_trad", "start_short", "start_long", 
              "shortLong_switch", "longShort_switch", "modTrad_switch",
              "tradMod_switch", "discontinuation")

for (i in 1:length(outcomes)) {
  country <- "mali"
  mali$outcome <- mali[[outcomes[i]]]
  print(paste0("Running...", outcomes[i]))
  model <- tidy(lm(outcome ~ 
            time*exposed_15 + 
            #cluster_unique +
            foreign_aid + 
            v501 + 
            v013 + 
            v025 + 
            v149 + 
            deaths + 
            v190, 
            data = mali))
    # model_glm <- lmer(outcome ~ 
    #         time*exposed_15 + 
    #         foreign_aid + 
    #         v501 + 
    #         v013 + 
    #         v025 + 
    #         v149 + 
    #         deaths + 
    #         v190 +
    #         (1|cluster_unique), 
    #         data = mali)
  model <- model %>%
  filter(str_detect(term, "time") == TRUE)
  write.csv(model, file = paste0("Results/", country, "_", outcomes[i], ".csv"))
}
```


# Model for Nigeria

## Loading data

```{r}
nigeria <- readRDS("DHS_data/Nigeria/Nigeria_final.RDS")
nigeria <- nigeria %>%
  select(c(abortion, conception, start, start_modern, start_trad, 
           start_short, start_long, shortLong_switch, longShort_switch, 
           modTrad_switch, tradMod_switch, discontinuation, Year, 
           exposed_15, v001, deaths, foreign_aid, v501, v013, v025, v149, 
           v190, cluster_unique)) %>%
    mutate(v501=as.character(v501),
         v013=as.character(v013),
         v025=as.character(v025),
         v149=as.character(v149),
         v190=as.character(v190),
         YearChar=as.character(Year)) %>%
  mutate(deaths = ifelse(is.na(deaths) == TRUE, 0, deaths))
```

## Running models

```{r}
outcomes <- c("abortion", "conception", "start", "start_modern", 
              "start_trad", "start_short", "start_long", 
              "shortLong_switch", "longShort_switch", "modTrad_switch",
              "tradMod_switch", "discontinuation")

for (i in 1:length(outcomes)) {
  country <- "nigeria"
  nigeria$outcome <- nigeria[[outcomes[i]]]
  print(paste0("Running...", outcomes[i]))
  model <- tidy(lm(outcome ~ 
            YearChar*exposed_15 + 
            #cluster_unique +
            foreign_aid + 
            v501 + 
            v013 + 
            v025 + 
            v149 + 
            deaths + 
            v190, 
            data = nigeria))
    # model_glm <- lmer(outcome ~ 
    #         Year*exposed_15 + 
    #         foreign_aid + 
    #         v501 + 
    #         v013 + 
    #         v025 + 
    #         v149 + 
    #         deaths + 
    #         v190 +
    #         (1|cluster_unique), 
    #         data = nigeria)
  model <- model %>%
  filter(str_detect(term, "Year") == TRUE)
  write.csv(model, file = paste0("Results/", country, "_", outcomes[i], ".csv"))
}
```

TODO:
- append the wave of survey to cluster variable in join data file in order to uniquely identify the cluster based on wave
- only interpret time exposed
- make all time coefficients relative to the during period
- for nigeria, have year*exposed_15 instead of time*exposed_15
- save and export each model output as csv in github, then group them by country
- put together table of estimates for just the interaction terms 
- make a line graph showing coefficient for each time period - marginal effects (https://cran.r-project.org/web/packages/margins/vignettes/Introduction.html)
  - add confidence intervals on graph
  - for nigeria, x is year, baseline is first year 
  - for mali and zimbabwe, time is x and have one value for exposed and unexposed
  
  
# Graphs

```{r}
library(coefplot)
```


```{r}
zim_model <- lm(start ~ 
            time*exposed_15 +
            foreign_aid + 
            v501 + 
            v013 + 
            v025 + 
            v149 + 
            deaths + 
            v190, 
            data = zimbabwe)

```

```{r}
library(ggplot2)
png(filename = "Results/Zimbabwe_file.png")
coefplot(zim_model, 
         coefficients = c("time3 years before:exposed_15", "time1 year before:exposed_15", "timeOnset:exposed_15", "timeEnd:exposed_15", "time1 year after:exposed_15", "time4 year after:exposed_15"), 
         title = "Contraceptive Uptake: Zimbabwe", 
         innerCI = 1.65, 
         outerCI = 2
         ) +
  scale_y_discrete(labels = c("Onset", "End", "4 years after", "3 years before", "1 year before", "1 year after")) + 
  scale_x_continuous(limits = c(-0.005, 0.0025)) +
  labs(subtitle = "Relative to During Conflict")
dev.off()
```


```{r}
mal_model <- lm(start ~ 
            time*exposed_15 +
            foreign_aid + 
            v501 + 
            v013 + 
            v025 + 
            v149 + 
            deaths + 
            v190, 
            data = mali)
```

```{r}
png(filename = "Results/Mali_file.png")
coefplot(mal_model, 
         coefficients = c("time3 years before:exposed_15", "time1 year before:exposed_15", "timeOnset:exposed_15"),
         title = "Contraceptive Uptake: Mali", 
         innerCI = 1.65, 
         outerCI = 2
         ) +
  scale_y_discrete(labels = c("Onset", "3 years before", "1 year before")) +
  scale_x_continuous(limits = c(-0.005, 0.0025)) +
  labs(subtitle = "Relative to During Conflict") 
dev.off()
```

```{r}
png(filename = "Results/Mali_file.png")
nig_model <- lm(start ~ 
            YearChar*exposed_15 + 
            foreign_aid + 
            v501 + 
            v013 + 
            v025 + 
            v149 + 
            deaths + 
            v190, 
            data = nigeria)
```

```{r}
coefplot(nig_model,
         coefficients = c("YearChar2009:exposed_15", "YearChar2010:exposed_15", "YearChar2011:exposed_15", "YearChar2012:exposed_15", "YearChar2013:exposed_15", "YearChar2014:exposed_15", "YearChar2015:exposed_15", "YearChar2016:exposed_15", "YearChar2017:exposed_15", "YearChar2018:exposed_15"),
         title = "Contraceptive Uptake: Mali", 
         innerCI = 1.65, 
         outerCI = 2
         ) +
  scale_y_discrete(labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018")) +
  scale_x_continuous(limits = c(-0.005, 0.0025)) +
  labs(subtitle = "Relative to 2008") 
dev.off()
```

  