---
title: "data_analysis"
author: "Shari Tian"
date: "2/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages

```{r}
library(tidyverse)
library(broom)
library(plm)
library(sf)
```


# Model

## Data

```{r}
zimbabwe <- readRDS("DHS_data/Zimbabwe/Zimbabwe_final.RDS")
zimbabwe <- zimbabwe %>%
  select(c(abortion, conception, start, start_modern, start_trad, 
           start_short, start_long, shortLong_switch, longShort_switch, 
           modTrad_switch, tradMod_switch, discontinuation, time, Year, 
           exposed_15, v001, deaths, foreign_aid, v501, v013, v025, v149, 
           v190, cluster_unique))
```

```{r}
models <- function(outcome, country){
  df <- readRDS(paste0("DHS_data/", country, "/", country, "_final.RDS")) 
  outcomes <- c("abortion", "conception", "start", "start_modern", 
                "start_trad", "start_short", "start_long", 
                "shortLong_switch", "longShort_switch", "modTrad_switch",
                "tradMod_switch", "discontinuation")
  model_tibble <- tibble(model = list())
  for(outcome in outcomes){
    model <- lm(outcome ~ time*exposed_15 + cluster_unique + deaths + 
                  foreign_aid + as.character(v501) + as.character(v013) + 
                  as.character(v025) + as.character(v149) + 
                  as.character(v190), data = df)
    model_tibble <- model_tibble %>% 
      add_row(model = model)
  }
} 
```

TODO:
- append the wave of survey to cluster variable in join data file in order to uniquely identify the cluster based on wave
- only interpret time exposed
- make all time coefficients relative to the during period
- for nigeria, have year*exposed_15 instead of time*exposed_15
- save and export each model output as csv in github, then group them by country
- put together table of estimates for just the interaction terms 
- make a line graph showing coefficient for each time period - marginal effects (https://cran.r-project.org/web/packages/margins/vignettes/Introduction.html)
  - add confidence intervals on graph
  - for nigeria, x is year, baseline is first year 
  - for mali and zimbabwe, time is x and have one value for exposed and unexposed 




```{r}
outcomes <- c("abortion", "conception", "start", "start_modern", 
              "start_trad", "start_short", "start_long", 
              "shortLong_switch", "longShort_switch", "modTrad_switch",
              "tradMod_switch", "discontinuation")

for (i in 1:length(outcomes)) {
  country <- "zimbabwe"
  model <- tidy(lm(paste(outcomes[i], " ~ time*exposed_15 + cluster_unique + 
                       foreign_aid + as.character(v501) + as.character(v013) + 
                       as.character(v025) + as.character(v149) + deaths + 
                       as.character(v190)"), data = zimbabwe))
  model <- model %>%
  filter(str_detect(term, "time") == TRUE)
  write.csv(model, file = paste0("Results/", country, "_", outcomes[i], ".csv"))
}
```
